Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-08 gibbs.tex
Apply 1 suggestion(s) to 1 file(s)

By the \emph{closed system} we mean that the gel is equlibrated with a \textbf{finite} reservoir, in this case after equilibration the gel and the reservoir again have the same ions chemical potential, the same temperature and desired pressure difference between the gel and the reservoir. 
Although, the number of ions and volume of gel and reservoir may vary, the total number of ions and the total volume are constant.

>>>>

By the \emph{closed system} we mean that the gel is equilibrated with a \textbf{finite} reservoir of an aqueous solution, in this case after equilibration the gel and the reservoir again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
Although, the number of ions and volume of gel and reservoir may vary, the total number of ions and the total volume are constant.
